Trends of SDR in Thessaloniki

### 2023-09-02 Article.Rmd
Commit 2023-09-02 17:10
Commit 2023-09-02 18:14

@@

```{r seasonalALL, echo=F, fig.cap="Trends by season for all condition. Displaying monthly means of daily means.", out.width="100%"}
knitr::include_graphics("./images/SeasonalTrendsTogether-1.png")
```

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]`          <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`           <- signif(pp$`Trend p-value`,  3)
pp$`Statistical signif. [%]` <- signif(pp$`Statistical signif. [%]`,  3)

@@

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       caption = "\\label{tab:trendseasontable}SDR trends of monthly anomaly for each season of the year. The vertical scale is common for all subplots, for easier comparison.")
```
<!-- \normalsize -->

>>>>

While in Spring and Summer the brightening of the SDR seem to be very low, although the statistical significance is now adequate for all cases, there are significant changes in Winter and Autumn
(Figure\ \ref{fig:seasonalALL} and Table\ \ref{tab:trendseasontable}).
Especially for winter and

@@

```{r seasonalALL, echo=F, fig.cap="SDR trends by season of the year for the three sky conditions. Each point is a monthly mean calculated from daily means. The vertical scale is common for all subplots, for easier comparison.", out.width="100%"}
knitr::include_graphics("./images/SeasonalTrendsTogether-1.png")
```

@@

<!-- \footnotesize -->
```{r trendseasontable, echo=F}
pp <- read.csv("./figures/tbl_longterm_trends_season.dat",
               strip.white = TRUE,
               sep = ";",
               header = TRUE)
pp <- pp[grep("SDR" ,pp$var), ]
pp$slope.sd           <- NULL
pp$slope.ConfInt_0.95 <- NULL
pp$slope.ConfInt_0.99 <- NULL
pp$var                <- NULL
rownames(pp)          <- NULL
names(pp) <- c("Trend [%/year]", "Trend p-value", "Sky condition", "Season", "Statistical signif. [%]")
## order by season
target    <- c("Winter", "Spring", "Summer", "Autumn")
new_order <- sapply(target, function(x,pp){which(pp$Season == x)}, pp=pp)
which(pp)
pp        <- pp[new_order,]
## numeric precision
pp$`Trend [%/year]`          <- signif(pp$`Trend [%/year]`, 3)
pp$`Trend p-value`           <- signif(pp$`Trend p-value`,  3)
pp$`Statistical signif. [%]` <- signif(pp$`Statistical signif. [%]`,  3)

@@

# panderOptions("table.alignment.default", "left")
panderOptions("table.alignment.default", "center")
pander(pp,
       justify = c('center', 'center', 'right', 'right', 'center'),
       split.table = Inf,
       caption = "\\label{tab:trendseasontable}SDR trends of monthly anomaly for each season of the year.")
```
<!-- \normalsize -->
